---
title: "Low Cost Sensor QC Weekly Report"
output:
    html_document:
      css: custom.css
      toc: yes
      self_contained: no
---
<!-- Added 'self_contained: no' so would run without error. It creates a folder that can be ignored --> 
<!-- Added the 'toc:yes' and css file to add a table of contents on the side for easier navigation --> 

<br>
<br>
<br>

```{r message=F, warning=F, echo=F}
################################################################################
#import latest version of full dataset
################################################################################
library(readr)

#version with site ID
fulldat <- read_csv("X:/Data/rawdata/sensor_data.csv")

```



#Completeness
```{r message=F, warning=F, echo=F}
################################################################################
# This code chunk loads the data for the past week and defines completeness functions
################################################################################

#set working directory to location of all files
setwd("X:/Production_Code/sensor_QC/")
source("completenessCode.R")

```


##Monitors Without Any Data From Last Week

```{r message=F,warning=FALSE, echo=F, results='asis'}
################################################################################
# This code chunk outputs a table with monitors that didn't collect any data for at least one day
################################################################################
library(knitr) #for kable()
library(kableExtra)
library(pander)

#get list of monitors
monitorlist<-getMonitorList(fulldat)

#get subset of data from last week
wk<-getLastWeek()

#get monitors without any data
missmonlist<-getMissingMonitors(monitorlist,wk)

#output lists with code right after chunk

```

*  **Unexpected to be missing:** <span style="color:red"> **`r c(missmonlist[missmonlist[,2]==0,1])`** </span>
<br>

*  Expected to have no data:  `r c(missmonlist[missmonlist[,2]==1 | missmonlist[,2]==2 ,1])`

<br>
(_Expectations based on location table in Access Database.  If that database is not up to date these monitors may be incorrectly categorized._)





<br>

##Lowest Completeness Proportions 
(_i.e. Monitors with at least one sensor measure having below 90% completeness_)

```{r message=F,warning=FALSE, echo=F, results='asis'}
################################################################################
# This code chunk outputs completeness tables with most important information
################################################################################

#get basic summary of worst behaving monitors
tab<-getBasicSummary(wk)
kable(tab,"html") %>%
   kable_styling(bootstrap_options = c("striped", "condensed")) %>%
    column_spec(1:4,  background = "lightgray") %>%
    column_spec(1,  color = "red", bold=T)



```

<br>
<br>
<br>
<br>
<br>
<br>

#Appendix

##Completeness
```{r message=F,warning=FALSE, echo=F, results='asis'}
################################################################################
# This code chunk outputs completeness tables for each Monitor (for the Appendix)
#    > Completeness for each sensor within mononitor for each day
################################################################################

#Add full completeness data for each monito
for(monitor in monitorlist){
  
  #add markdown header for monitor (Note: we added a floating toc to account for the massive toc size)
  pandoc.header(monitor,level=3)

  #get table with all monitor data
  tab<-getMonitorCompleteness(monitor,wk)
  
  #only give comments on table if actually have data
  if(!is.null(dim(tab)) ){
      Pandoc.brew(text="*  The first row gives the total possible observations for the week/day. ")
      Pandoc.brew(text="*  Each cell in the rest of the table shows the *complete observations (Percent complete)* for the specified sensor.")
  }
  
  #print table
  print(kable(tab,row.names = FALSE,format = "html") %>%
   kable_styling(bootstrap_options = c("striped", "condensed")) %>%
    row_spec(1,  background = "lightgray") )
}


```



















<!-- Add the date of the title at the end to data from the r chunks --> 

---
date: "`r paste0("Data from ",format(min(as.Date(as.POSIXlt(wk$date))),"%m-%d-%Y")," through  ", format(max(as.Date(as.POSIXlt(wk$date))),"%m-%d-%Y")  )
`"
---