---
title: "Low Cost Sensor QC Weekly Report"
output:
    html_document:
      css: custom.css
      toc: yes
      self_contained: no
---
<!-- Added 'self_contained: no' so would run without error. It creates a folder that can be ignored --> 
<!-- Added the 'toc:yes' and css file to add a table of contents on the side for easier navigation --> 





<br>
<br>
<br>

```{r message=F, warning=F, echo=F}
################################################################################
#import latest version of full dataset
################################################################################
library(readr)
fulldat<- read_csv("X:/Data/rawdata/sensor_data.csv")

```



#Completeness
```{r message=F, warning=F, echo=F}
################################################################################
# This code chunk loads the data for the past week and defines completeness functions
################################################################################

#set working directory to location of all files
setwd("X:/Production_Code/sensor_QC/")
source("completenessCode.R")

```


##Monitors Without Any Data For One or More Days Last Week
(_i.e. Monitors which didn't have any data (not even NA's), due to transimssion issues or being serviced etc._)

```{r message=F,warning=FALSE, echo=F, results='asis'}
################################################################################
# This code chunk outputs a table with monitors that didn't collect any data for at least one day
################################################################################
library(knitr) #for kable()
library(kableExtra)

#get list of monitors
monitorlist<-getMonitorList(fulldat)

#get subset of data from last week
wk<-getLastWeek()

#get monitors with some days missing from last week
tab<-getMissingMonitors(monitorlist,wk)
kable(tab,"html") %>%
   kable_styling(bootstrap_options = c("striped", "condensed"))

```


##Lowest Completeness Proportions 
(_i.e. Monitors with at least one sensor measure having below 90% completeness_)

```{r message=F,warning=FALSE, echo=F, results='asis'}
################################################################################
# This code chunk outputs completeness tables with most important information
################################################################################

#get basic summary of worst behaving monitors
tab<-getBasicSummary(wk)
kable(tab,"html") %>%
   kable_styling(bootstrap_options = c("striped", "condensed")) %>%
    column_spec(6,  background = "gold")


```

<br>
<br>
<br>
<br>
<br>
<br>

#Appendix

##Completeness
```{r message=F,warning=FALSE, echo=F, results='asis'}
################################################################################
# This code chunk outputs completeness tables for each Monitor (for the Appendix)
#    > Completeness for each sensor within mononitor for each day
################################################################################

library(pander) #to create markdown header outputs

#Add full completeness data for each monito
for(monitor in monitorlist){
  
  #add markdown header for monitor (Note: we added a floating toc to account for the massive toc size)
  pandoc.header(monitor,level=3)

  #print table
  tab<-getMonitorCompleteness(monitor,wk)
  print(kable(tab))
}


```



















<!-- Add the date of the title at the end to data from the r chunks --> 

---
date: "`r paste0("Data from ",format(min(as.Date(as.POSIXlt(wk$date))),"%m-%d-%Y")," through  ", format(max(as.Date(as.POSIXlt(wk$date))),"%m-%d-%Y")  )
`"
---